---
title: "Diss"
author: "Noah Byrne"
date: "2025-07-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Movement:
- Random: angle (rwrappedcauchy()) and distance (lognormal distribution)
- Avoidance: angle (rwrappedcauchy()) and distance (Uniform dist. value multiplied by difference b/n max. distance from transect & animal distance from transect)

*The purpose of calculating avoidance distance in this way is so that animals that are closest to the transect move the farthest. (scaled by 2.5 to make avoidance case comprable to avoidance case)

Avoidance:
```{r}
circular(0) # The value in brackets describes the "zero" argument of this function
plot(circular(0))
```
Random:
```{r}
circular(pi)
plot(circular(pi))
```
```{r}
num <- nrow(df[df$x <= 0 & df$obs==1, ])
rwrappedcauchy(n = num, mu = circular(0), rho = 0, control.circular = list(units= "radian"))
```
Imperfect Matching:
- using the "sim.mismatch" function
- find distance between 1st occasion animals and all 2nd occasion animals
- match 2nd occasion animals TO closest animal from first occasion
      - HOW DO WE DECIDE THIS?
        - WITHIN 300 METERS is the same individual
        - BETWEEN 300 AND 1000 METERS is determined with inverse power function             (f^-1(x) = cuberoot(x))
        - OVER 1000 METERS is a different individual
      - same individuals have both entries combined into ONE data frame entry
      - new individuals are added as TWO SEPARATE data frame entries
      
